%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Bosch Global Software Technologies Viet Nam}
{Consultant}
{Ho Chi Minh City, Vietnam}
{Apr. 2019 - Ongoing}
{
\begin{cvitems}
\item {Involved in the UI \& UX enhancement for the product despite the lack of support for the extensibility on the Standard SAP Fiori Apps.}
\item {Responsible for SAP UI5 Component development and User Interface customization based on customer requirements.}
\item {Built the Side-by-Side extension development competency to adapt new technologies on SAP Business Technology Platform.}
\item {Led Google Analytics integration topics on SAP Fiori apps to track front-end and OData services performance.}
\item {Researched and integrated Microsoft Power Platform technologies with SAP on-premise systems via SAP ERP connector, OData services and custom RFCs.}
\item {Contributed to the competency development of non-SAP technology such as Web Development with Node.js, Internet of Things, and Machine Learning.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{DXC Technology Vietnam}
{Associate Software Engineer}
{Ho Chi Minh City, Vietnam}
{Mar. 2016 - Apr. 2019}
{
\begin{cvitems}
\item {Built responsive web components that well-tested with React, Styled Component, Jest, Enzyme and integrated with Next.js and Express.js powered corporation websites..}
\item {Developed hybrid application that runs on cross-platform integrated with government healthcare system with Ionic, Angular, and RxJS.}
\item {Experienced in working in Agile environment with colleagues from different countries.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{webfire}
{Web Developer}
{London, United Kingdom}
{Sep. 2014 - Dec. 2015}
{
\begin{cvitems}
\item {Built many websites use HTML, CSS, jQuery, PHP, and WordPress.}
\item {Collaborated directly with the product owner to transfer the graphic design to custom CMS.}
\end{cvitems} 
}

%------------------------------------------------

\cventry
{brick\&mobile}
{Web Developer}
{Toronto, Canada}
{Feb. 2014 - Aug. 2014}
{
\begin{cvitems}
\item {Customized RADIUSdesk based on CodeIgniter uses PHP, MySQL, and Facebook API for Social Wi-Fi Marketing solution.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{BusyNeed}
{Software Developer Intern}
{Ho Chi Minh City, Vietnam}
{Oct. 2012 - Dec. 2012}
{
\begin{cvitems}
\item {Built RESTful web services use WCF for web crawling platform.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}