%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Projects}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Bosch Global Software Technologies Viet Nam}
{Kanban Write}
{}
{}
{
\begin{cvitems}
\item {An Fiori application that deployed on SAP Business Technology Platform to update KANBAN Write Tag for devices from SAP on-premise systems. The application is deployed through CI/CD on SAP Business Technology Platform.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Bosch Global Software Technologies Viet Nam}
{Supplier Self Service}
{}
{}
{
\begin{cvitems}
\item {An important feature in Supply Chain Management allowing Business Partners from Supply-On to update critical information including personal data and bank account onto on-premises systems. The solutions significantly reduce paper works and keep consistent user experience between 3rd platform and in-house applications.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Bosch Global Software Technologies Viet Nam}
{Lincoln Sentry}
{}
{}
{
\begin{cvitems}
\item {A B2B platform that built on SAP Commerce and integrated with SAP on-premise system for Dulux Group.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Bosch Global Software Technologies Viet Nam}
{Unified Inbox}
{}
{}
{
\begin{cvitems}
\item {One-stop platform to view and approve workflow items for top-level managers with SAP Gateway, SAP UI5, Elasticsearch, and multiple source systems.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{AXA Singapore}
{Corporation Website}
{}
{}
{
\begin{cvitems}
\item {Transformed legacy PHP website to cutting-edge technologies with Next.js, React, Styled Component, Node.js, and Prismic.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{AXA Singapore}
{Fund Price}
{}
{}
{
\begin{cvitems}
\item {The application helps customers fast and easy access to all fund information with chart data visualization built with React, Redux, Express.js, and MongoDB.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{DXC Technology}
{Lorenzo ClinicalAide}
{}
{}
{
\begin{cvitems}
\item {Hybrid application unifies various hospital systems so physicians can treat and track their patients using an Android, iOS or Windows device.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}