\PassOptionsToPackage{dvipsnames}{xcolor}
\documentclass[10pt,a4paper,ragged2e]{altacv}
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm}

\ifxetexorluatex
  \setmainfont{Carlito}
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
\fi

\definecolor{Mulberry}{HTML}{72243D}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{Sepia}
\colorlet{accent}{Mulberry}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\begin{document}
\name{Duong Minh Nhut}
\tagline{Front-End Web Developer}
\personalinfo{
  \email{nhutdm@gmail.com}
  \phone{0987-195-190}
  \mailaddress{18B1/22 Pham Hung St}
  \location{Ho Chi Minh City, Vietnam}
}

\begin{fullwidth}
\makecvheader
\end{fullwidth}

\cvsection[page1sidebar]{Summary}
A front-end web developer with more than 5 years of experience building websites, hybrid applications in fast-paced, collaborative environments. Highly skilled in React, Angular, HTML, CSS and JavaScript.

\cvsection{Experience}
\cvevent{Software Engineer}{DXC Technology}{Jan 2016 -- Ongoing}{Ho Chi Minh City, Vietnam}
\begin{itemize}
\item Built responsive web components that well-tested with React, Styled Component, Jest, Enzyme and integrated with Next.js and Express.js powered corporation websites.
\item Developed hybrid application that runs on cross-platform integrated with government healthcare system with Ionic, Angular, and RxJS.
\item Experienced in working in Agile environment with colleagues from different countries.
\end{itemize}
\divider

\cvevent{Web Developer}{webfire}{Sep 2014 -- Dec 2015}{London, United Kingdom}
\begin{itemize}
\item Built many websites use HTML, CSS, jQuery, PHP, and WordPress.
\item Collaborated directly with the product owner to transfer the graphic design to custom CMS.
\end{itemize}
\divider

\cvevent{Web Developer}{brick\&mobile}{Feb 2014 -- Aug 2014}{Toronto, Canada}
\begin{itemize}
\item Customized RADIUSdesk based on CodeIgniter uses PHP, MySQL, and Facebook API for Social Wi-Fi Marketing solution.
\end{itemize}
\divider

\cvevent{Software Developer Intern}{BusyNeed}{Oct 2012 -- Dec 2012}{Ho Chi Minh City, Vietnam}
\begin{itemize}
\item Built RESTful web services use WCF for web crawling platform.
\end{itemize}

\cvsection{Education}

\cvevent{Bachelor of Science in Computing}{University of Greenwich}{Nov 2012 -- Jul 2014}{Ho Chi Minh City, Vietnam}
\divider

\cvevent{Higher Diploma in Software Engineering}{Aptech Computer Education}{Jun 2010 -- Aug 2011}{Ho Chi Minh City, Vietnam}
\divider

\cvevent{Diploma in Information Systems Management}{Aptech Computer Education}{Jul 2009 -- Aug 2010}{Ho Chi Minh City, Vietnam}

\clearpage

\cvsection[page2sidebar]{Certificates}

\cvevent{Test of English for International Communication}{Educational Testing Service}{Apr 2018}{Ho Chi Minh City, Vietnam}
\begin{itemize}
\item Listening: 345.
\item Reading: 445.
\end{itemize}
\divider

\cvevent{Scrum Master Accredited Certification}{International Scrum Institute™}{Dec 2016}{Ho Chi Minh City, Vietnam}
\divider

\cvevent{M101JS: MongoDB for Node.js Developers}{MongoDB}{Dec 2016}{Ho Chi Minh City, Vietnam}

\cvsection{Extracurricular Activities}

\cvevent{Elite Member}{Hacker Vietnam Association}{Jun 2003 -- Sep 2014}{Ho Chi Minh City, Vietnam}
\begin{itemize}
\item Performed troubleshooting of members' issues.
\item Focused on web application exploits and vulnerabilities.
\item Contributed articles about AutoIt for automation on MS Windows.
\end{itemize}

\end{document}
